MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-25 paper.Rmd
SEA --> R
Minor edit.

We created a suite of `R` packages 
(some of which are generally useful and available through 
[CRAN][link-cran],
others of which are focused on SEA and available on GitHub)
to assist SEA practitioners as they analyze 
energy movement through society. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the packages enable, for the first time, scalable SEA.
We used the new packages to create the "PFU Database,"^[Strictly speaking, 
we create data frames of matrices, 
not an SQL or similar database.] 
a new resource for the SEA community [@Marshall:2023aa].

@@

The most important decision for the design of the suite of SEA packages
involves data format.
We authors are among those who
developed the Physical Supply-Use Table (PSUT) framework,
a matrix-based approach to describing energy flows 
("products" in PSUT terminology) 
from resource extraction to
processing stages
("industries" in PSUT terminology)
and, ultimately, 
to final demand [@Rocco:2016; @Guevara:2017; @Heun:2018; @Aramendia:2022tv].
We chose the PSUT framework as the data format for the `R` packages, 
because it succinctly describes an entire ECC
via a set of six matrices described in the following table.

>>>>

We created a suite of `R` packages 
(some of which are generally useful and available through 
[CRAN][link-cran],
others of which are focused on SEA and available on GitHub)
to assist SEA practitioners as they analyze 
energy movement through society. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the packages enable, for the first time, scalable SEA.
We used the new packages to create the "PFU Database,"^[Technically speaking, 
we create data frames of matrices, 
not an SQL or similar database.] 
a new resource for the SEA community [@Marshall:2023aa].

@@

The most important decision for the design of the suite of `R` packages
involves data format.
We authors are among those who
developed the Physical Supply-Use Table (PSUT) framework,
a matrix-based approach to describing energy flows 
("products" in PSUT terminology) 
from resource extraction to
processing stages
("industries" in PSUT terminology)
and, ultimately, 
to final demand [@Rocco:2016; @Guevara:2017; @Heun:2018; @Aramendia:2022tv].
We chose the PSUT framework as the data format for the `R` packages, 
because it succinctly describes an entire ECC
via a set of six matrices described in the following table.
